Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation

### 2024-12-04 paper/paper.qmd
Update paper.qmd

After introducing the source and background of the data, here we will explain how to use the `R` language [@citeR] functions and some additional packages learned in the course to process the data. Here is a unified overview. The `dplyr` package [@dplyr] is a grammar of data manipulation, providing a consistent set of verbs that help us solve the most common data manipulation challenges. In this package, this article mainly uses the `mutate` function and the `filter`function, where the `mutate`[@dplyrMutate] function creates new columns that are functions of existing variables. The `filter` [@dplyrFilter] function is used to subset a data frame, retaining all rows that satisfy conditions.In the visualization stage, this article uses the `ggplot2`[@ggplot2] package to draw graphics, and when analyzing the results, in order to see the output results more intuitively, this article also uses the `xtable`[@xtable] package to convert the results into `LaTex` format for output. Finally, in order to output the variable data that needs to be analyzed, this article also draws on the `arrow`[@arrow] package recommended in the course to output data in `parquet` format, and other Key libraries that supported the data analysis include `readxl`[@readxl], ggbeeswarm`[@ggbeeswarm], `tidyverse`[@tidyverse], `patch`[@patch], `bayesplot`[@bayesplot], `rstanarm`[@rstanarm]. Also this analysis inherits the folder structure from Professor Rohan Alexander from University of Toronto [@Rohan].

>>>>

After introducing the source and background of the data, here we will explain how to use the `R` language [@citeR] functions and some additional packages learned in the course to process the data. Here is a unified overview. The `dplyr` package [@dplyr] is a grammar of data manipulation, providing a consistent set of verbs that help us solve the most common data manipulation challenges. In this package, this article mainly uses the `mutate` function and the `filter`function, where the `mutate`[@dplyrMutate] function creates new columns that are functions of existing variables. The `filter` [@dplyrFilter] function is used to subset a data frame, retaining all rows that satisfy conditions.In the visualization stage, this article uses the `ggplot2`[@ggplot2] package to draw graphics, and when analyzing the results, in order to see the output results more intuitively, this article also uses the `xtable`[@xtable] package to convert the results into `LaTex` format for output. Finally, in order to output the variable data that needs to be analyzed, this article also draws on the `arrow`[@arrow] package recommended in the course to output data in `parquet` format, and other Key libraries that supported the data analysis include `readxl`[@readxl], `ggbeeswarm`[@ggbeeswarm], `tidyverse`[@tidyverse], `patch`[@patch], `bayesplot`[@bayesplot], `rstanarm`[@rstanarm]. Also this analysis inherits the folder structure from Professor Rohan Alexander from University of Toronto [@Rohan].
